Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-07-16 STAT-paper-template/APA/fertile.Rnw
addressing hadley comment

A small body of papers and \R packages focusing on reproducibility in the \R community have been published. Much of this work is narrowly tailored, with each package effectively addressising a small component of reproducibility: file structure, modularization of code, version control, etc. Many existing reproducibility packages, due to their focused nature, succeed at their area of focus, but at a cost. They are often difficult to learn and operate, providing a barrier to entry for less-experienced data analysts.

There appear to be no existing tools that cater to analysts looking for an easy-to-learn, easy-to-implement, fast, way to obtain a broad overview of their projects' reproducibility. To address this, we present an \R package called \pkg{fertile}, a low barrier-to-entry package which focuses on a series of common mistakes programmers make while conducting data science research in R.

>>>>

A small body of papers and \R packages focusing on reproducibility in the \R community have been published. Much of this work is narrowly tailored, with each package effectively addressising a small component of reproducibility: file structure, modularization of code, version control, etc. Many existing reproducibility packages, due to their focused nature, succeed at their area of focus, but at a cost. They are often difficult to learn and operate, providing a barrier to entry for less-experienced data analysts. This can make the goal of achieving reproducibility unnecessarily challenging, leading to users becoming discouraged and deciding that the effort necessary to succeed is not worth it.

A much more effective way to achieve widespread reproducibility is to make the process for doing so simple enough so that it takes next to no conscious effort to implement. However, there appear to be no existing tools that fit this model--catering to analysts looking for an easy-to-learn, easy-to-implement, fast, way to obtain a broad overview of their projects' reproducibility. To address this, we present an \R package called \pkg{fertile}, a low barrier-to-entry package which focuses on a series of common mistakes programmers make while conducting data science research in R.
